---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# drealdown

<!-- badges: start -->
<!-- badges: end -->

This is package {drealdown}: Templates for html outputs.
You are using version 0.0.0.9000.

## Installation

The list of dependencies required to install this package is:
```{r, echo=FALSE}
attachment::att_from_description()
```

To install the package, you can run the following script

``` {.r}
# install.packages("remotes")
remotes::install_git(url = "https://git.thinkr.fr/ThinkR/Missions/drealdown")
```

## Templates

### Voir tous les exemples inclus

```{r, eval=FALSE}
examples <- system.file("examples", package = "drealdown")
browseURL(examples)
```

### Fonctions incluses

- Markdown classique de type `rmarkown::html_document()` : `drealdown::html_mark()`
- Markdown avancé avec bookdown de type `bookdown::html_document2()` : `drealdown::html_book2()`
- Markdown pour vignette de type `rmarkdown::html_vignette()` : `drealdown::html_vignette()`
